WORCS: A Workflow for Open Reproducible Code in Science

### 2020-10-28 paper/reviews_ds.Rmd
Address R1 comment user evaluation required

>>>>

Response: In addressing this comment, we respectfully refer to our response to the preceding comment ("There is no user evaluation", R1), and again emphasize the Editor's comment that "resource papers do not need to have a full-blown user evaluation". We would also like to clarify that the goal of the present manuscript is to define the problem worcs intends to address (specifically; meeting the TOP-guidelines for Open Science), introduce the tools worcs uses to address this problem, explain how worcs uses these tools, and provide a step-by-step workflow. It is not clear what "claims" are made that are unsupported by evidence. In the revision, we have attempted to further clarify this goal from the paper onset: REF.

We do take the suggestion of performing a user evaluation very seriously, but in our mind, this is a next step. First, the workflow must be published, then it can be taught, and subsequently evaluated.

\Assignment{CJ}
\Done
\Easy
